### 2020-02-20 Article.tex
FindeZgZ

Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
by $G_n$.

\begin{definition}
	Let $\Sigma$ be a set, let $\mathcal{F}:=\{H_1, \dots, H_l\}$
	be a finite family of hypergraphs, and
	for each $n\in \N$ let $\chi_n$ be a random coloring of $G_n$. We say that 
	$\chi_n$ is asymptotically $\mathcal{F}$-invariant if for any 
	\begin{itemize}
		\item fixed finite number of copies of hypergraphs from 
		$\mathcal{F}$ in $\N$,
		$G^1,\dots, G^k \in Copies(\N,H_1)\cup \dots \cup Copies(\N,H_l)$.
		\item fixed vertices $\overbrace{v}\in G^1,\dots,G^k$.
		\item fixed labels $\overbar{s}\in \Sigma$
	\end{itemize}  
\end{definition}

\begin{theorem} 
	Let $v_1,\dots, v_k\in \N$ be different vertices and let 
	$\Sigma_1,\dots,\Sigma_k$ be finite sets. For each 
	$i\in [k]$ let $\mathcal{T}_i$ be a finite set of non-superimposable
	rooted $\Sigma_i$-trees. 
	For each $n\in N$ and $i\in [k]$ let $\chi_{n,i}$ be a random 
	$\Sigma_i$ coloring over $G_n$ such that for any $w\in \N$ and any $S \in \Sigma_i$
	the limit
	\[
	\Ln \mathrm{Pr}\big( \chi_n(w)=S\big)
	\]
	exists and does not depend on the chosen $w$. For each 
	$S \in \Sigma_i$, let $\mu_{i,S}$ denote last limit. 
	Given a tree $T\in \mathcal{T}_i$ let
	\[
	\lambda_{i,T}=\frac{1}{|Aut(T)|}\prod_{S\in \Sigma_i} \mu_{i,S}^{v(S,T)} 
	\]	
\end{theorem}

>>>>

Remark: A random coloring $\chi$ of $G_n$ does not have to be independent from
$G_n$. In fact, in the cases we are going to consider $\chi$ will be determined
by $G_n$. \par

For each $n\in \N$ let $\chi_n$ be a random $\Sigma$-coloring of $G_n$. 
We say that the sequence $\chi_n$ is regular if:
\begin{itemize}
	\item[(1)] For each $n\in \N$ and $s\in \Sigma$ the probability 
	$\mathrm{Pr}\big(\chi_n(v)=s\big)$ is the same for all vertices
	$v\in [n]$. 
	\item[(2)] For any vertex $v\in \N$ and any $s\in \Sigma$, the limit 
	$\Ln \mathrm{Pr}\big(\chi_n(v)=s\big)$ exists. Notice that condition (1) implies
	that this limit does not depend on $v$.
\end{itemize}
If the $\chi_n$'s form a regular sequence of colorings we will write
$\mathrm{Pr}[\chi,s]$ to denote the limit $\Ln \mathrm{Pr}\big(\chi_n(v)=s\big)$
in (2).

\begin{definition}
	Let $\mathcal{F}$
	be a family of hypergraphs, and for each $i\in [l]$
	let $(\chi_{n,i})_{n\in \N}$ be a sequence of regular 
	random	$\Sigma_i$-colorings of $G_n$. We say that the sequences 
	$(\chi_{n,i})$ are asymptotically stable with respect to $\mathcal{F}$
	if for any 
	\begin{itemize}
		\item fixed finite number of copies of hypergraphs from 
		$\mathcal{F}$ in $\N$,
		$G^1,\dots, G^k \in \bigcup_{H\in \mathcal{F}} Copies(\N,H)$,
		\item fixed different vertices $v_1, \dots, v_a \in V(G^1)\cup\dots \cup V(G^k)$,
		indices $i_1,\dots, i_a \in [l]$ and labels $s_1 \in \Sigma_{i_1},\dots, s_a\in
		\Sigma_{i_a}$,
	\end{itemize}  
	it is satisfied that
	\[
	\Ln \mathrm{Pr}\big(
	\bigwedge_{c=1}^l \chi_{n,i_c}(v_c)= s_c  \, \big| \, \bigwedge_{j=1}^k G^j \subset G_n 
	\big)= \prod_{c=1}^{l} \mathrm{Pr}[\chi_{i,c},s_c].	
	\]
\end{definition}

\begin{theorem}
	Let $l\in \N$. For any $i\in [l]$ 
	\begin{itemize}
	\item Let $\Sigma_i$ be a set of colors. 
	\item Let $H_i$ be a unicycle and let $\eta_i$
	be a $\Sigma_i$-coloring of
	$H_i$.
	\item Let $(\chi_{n,i})_{n\in \N}$ be a regular
	sequence of random $\Sigma_i$-colorings
	of $(G_n)_{n\in \N}$.
	\item Let $X_{n,i}$ be the random variable that
	counts the copies of $(H_i, \eta_i)$ in $(G_n,
	\chi_{n,i})$.
	\end{itemize}
	Let $\mathcal{F}=\{H_1,\dots,H_l\}$. Suppose the
	sequences $(\chi_{n,i})$ are asymptotically stable
	with respect to $\mathcal{F}$. Then the random variables
	$X_{n,i}$ are asymptotically distributed like independent Poisson 
	variables with means 
	\[\lambda_i:= \frac{\left(\prod_{i=1}^t \beta_i^{e_i(H_i)}\right) \left(
	\prod_{s\in \Sigma_i} \mathrm{Pr}[\chi_i,s]^{|\eta^{-1}(s)|}	\right) }
	{|Aut(H_i,\eta_i)|}. 
  	\]
  	That is, given any $b_1,\dots,b_l \in \N$,
  	\[
  	\Ln \mathrm{Pr}\big( 
  	\bigwedge_{i=1}^l X_{n,i}=b_i
  	\big) = \prod_{i=1}^l e^{-\lambda_i}\frac{\lambda_i^{b_i}}{b_i!}.
  	\] 
\end{theorem}	
\begin{proof}
	We have to show that for any $c_1, \dots, c_l\in \N$
	\begin{equation}\label{eqn:aux2}
	\Ln  \mathrm{E}\big[
	\prod_{i=1}^l (X_{n,i})_{c_i}
	\big] = \prod_{i=1}^l \lambda_i^{c_i}.
	\end{equation}
	Then using \cref{thm:BrunSieve} the theorem follows.\par
	For any $i\in [l]$, the random variable $(X_{n,i})_{c_i}$
	counts the number of ordered tuples 
	$(H_i^1,\eta_i^1),\dots,$ $(H_i^{c_i},\eta_i^{c_i})$ such that
	for each $j\in [c_i]$, $(H_i^j,\eta_i^j)\subset
	(G_n,\chi_{n,i})$. Let 
	$\Omega=\prod_{i=1}^{l}[Copy((H_i,\eta_i),[n])]_{c_i}$ 
	\[
	\mathrm{E}\big[
	\prod_{i=1}^l (X_{n,i})_{c_i}
	\big]\]

\end{proof}
